\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}

\usepackage[a4paper,left=3cm,right=3cm,bottom=2.5cm,top=2.5cm]{geometry}

\usepackage{style}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{tabularx}
\robustify\cftdotfill
\usepackage{hyperref}       % hyperlinks

\usepackage{fontawesome}

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

\newcommand{\resheading}[1]{
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[5.662in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[2]{
\begin{tabularx}{\textwidth}{Xr}
  #1 & #2
\end{tabularx}
}

\begin{document}

\begin{tabularx}{\textwidth}{Xr}
  \textbf{\huge Matthias Fey}\\
  \vspace{-0.2cm}
  \faBirthdayCake~02.06.1990 in Unna, Deutschland\\
  \faMapMarker~Von-der-Recke-Str. 9, 44137 Dortmund, Deutschland\\
  \faEnvelope~\url{matthias.fey@tu-dortmund.de}\\
  \faPhone~+49~160~3032292\\
  \faBookmark~\url{https://rusty1s.github.io}\\
\end{tabularx}

\resheading{Ausbildung}

\ressubheading{\textbf{Doktor der Ingenieurwissenschaften}\\ an der Technischen Universtität Dortmund}{\faCalendar~\emph{2017 - 2022}}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \small \textbf{Themen:} Geometric Deep Learning \& Graph Representation Learning
  \item \small \textbf{Titel:} On the Power of Neural Message Passing for Learning on Graph-Structured Data
  \item \small \textbf{Doktorvater:} Priv.-Doz.~Dr.~Frank Weichert
  \item \small Abschluss mit summa cum laude
\end{itemize}

\ressubheading{\textbf{M.S. in Informatik} an der Technischen Universität Dortmund}{\faCalendar~\emph{2013 - 2017}}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \small \textbf{Titel:} Convolutional Neural Networks auf Graphrepräsentationen von Bildern
  \item \small Abschluss mit Auszeichnung
\end{itemize}

\ressubheading{\textbf{B.S. in Informatik} an der Technischen Universität Dortmund}{\faCalendar~\emph{2010 - 2013}}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \small \textbf{Titel:} Qualitative Semantiken für DAGs – ein Vergleich von OCF- und CP-Netzwerken
\end{itemize}

\ressubheading{\textbf{Abitur} am Pestalozzi Gymnasium, Unna}{\faCalendar~\emph{2000 - 2009}}

\resheading{Tätigkeiten}

\ressubheading{\textbf{Gründungs-Ingenieur} bei Kumo.ai, San Francisco, California}{\faCalendar~\emph{2022 - aktuell}}

\ressubheading{\textbf{Wissenschaftlicher Mitarbeiter}\\ an der Technischen Universität Dortmund}{\faCalendar~\emph{2017 - 2021}}
\begin{itemize}
  \setlength\itemsep{0em}
  \item \small \textbf{SFB 876, Project A6:} Resource-efficient Graph Mining
  \item \small \textbf{Lehrkraft:} Mensch-Maschine-Interaktion
\end{itemize}

\ressubheading{\textbf{Software-Ingenieur} bei Comline, Dortmund}{\faCalendar~\emph{2013 - 2017}}

\ressubheading{\textbf{Zivildienst} am Katharinen Hospital, Unna}{\faCalendar~\emph{2009 - 2010}}

\resheading{Forschungsaufenthalte}

\ressubheading{\textbf{Stanford University}\\ im SNAP-Lab mit Jure Leskovec, Stanford, California}{\faCalendar~\emph{Feb 2020 - Mar 2020}}

\resheading{Auszeichnungen}

\ressubheading{\textbf{Dissertationspreis} der Alumni, Dortmund}{\faCalendar~\emph{2022}}

\resheading{Veröffentlichungen}

\ressubheading{Christopher Morris, Yaron Lipman, Haggai Maron, Bastian Rieck, Nils M. Kriege, Martin Grohe, \textbf{Matthias Fey} and Karsten Borgwardt: Weisfeiler and Leman go Machine Learning: The Story so far. In: \emph{CoRR, abs/2112.09992}}{\faCalendar~\emph{2021}}

\ressubheading{\textbf{Matthias Fey}, Jan Eric Lenssen, Frank Weichert and Jure Leskovec: GNNAutoScale: Scalable And Expressive Graph Neural Networks via Historical Embeddings. In: \emph{International Conference on Machine Learning (ICML)}.}{\faCalendar~\emph{2021}}

\ressubheading{Weihua Hu, \textbf{Matthias Fey}, Hongyu Ren, Maho Nakata, Yuxiao Dong and Jure Leskovec: OGB-LSC:\@ Large-Scale Challenge for Machine Learning on Graphs. In: \emph{NeurIPS:\@ Datasets and Benchmarks Track}.}{\faCalendar~\emph{2021}}

\ressubheading{Christopher Morris, \textbf{Matthias Fey}, Nils M. Kriege: The Power of the Weisfeiler-Leman Algorithm for Machine Learning with Graphs. In: \emph{International Joint Conference on Artificial Intelligence (IJCAI) --- Survey Track}.}{\faCalendar~\emph{2021}}

\ressubheading{\textbf{Matthias Fey*}, Jan-Gin Yuen* and Frank Weichert: Hierarchical Inter-Message Passing for Learning on Molecular Graphs. In: \emph{ICML Workshop on Graph Representation Learning and Beyond (GRL+)}.}{\faCalendar~\emph{2020}}

\ressubheading{Marian Kleineberg, \textbf{Matthias Fey} and Frank Weichert: Adversarial Generation of Continuous Implicit Shape Representations. In: \emph{Eurographics.}}{\faCalendar~\emph{2020}}

\ressubheading{Weihua Hu, \textbf{Matthias Fey}, Marinka Zitnik, Yuxiao Dong, Hongyu Ren, Bowen Liu, Michele Catasta and Jure Leskovec: Open Graph Benchmark: Da\-ta\-sets for Machine Learning on Graphs. In: \emph{Advances in Neural Information Processing Systems (NeurIPS)} \textbf{(spotlight)}.}{\faCalendar~\emph{2020}}

\ressubheading{\textbf{Matthias Fey}, Jan Eric Lenssen, Christopher Morris, Jonathan Masci and Nils M. Kriege: Deep Graph Matching Consensus. In: \emph{International Conference on Learning Representations (ICLR)}.}{\faCalendar~\emph{2020}}

\ressubheading{\textbf{Matthias Fey}: Just Jump: Dynamic Neighborhood Aggregation in Graph Neural Networks. In: \emph{ICLR Workshop on Representation Learning on Graphs and Manifolds (RLGM)}.}{\faCalendar~\emph{2019}}

\ressubheading{\textbf{Matthias Fey} and Jan Eric Lenssen: Fast Graph Representation Learning with PyTorch Geometric. In: \emph{ICLR Workshop on Representation Learning on Graphs and Manifolds (RLGM)} \textbf{(contributed talk)}.}{\faCalendar~\emph{2019}}

\ressubheading{Christopher Morris, Martin Ritzert, \textbf{Matthias Fey}, William L. Hamilton, Jan Eric Lenssen, Gaurav Rattan and Martin Grohe: Weisfeiler and Leman Go Neural: Higher-Order Graph Neural Networks. In: \emph{Conference on Artificial Intelligence (AAAI)}.}{\faCalendar~\emph{2019}}

\ressubheading{Jan Eric Lenssen, \textbf{Matthias Fey} and Pascal Libuschewski: Group Equivariant Capsule Networks. In: \emph{Advances in Neural Information Processing Systems (NeurIPS).}}{\faCalendar~\emph{2018}}

\ressubheading{Nils M. Kriege, \textbf{Matthias Fey}, Denis Fisseler, Petra Mutzel and Frank Weichert: Recognizing Cuneiform Signs Using Graph-Based Methods. In: \emph{SDM Workshop on Cost-Sensitive Learning (COST).}}{\faCalendar~\emph{2018}}

\ressubheading{\textbf{Matthias Fey*}, Jan Eric Lenssen*, Frank Weichert and Heinrich Müller: SplineCNN:\@ Fast Geometric Deep Learning with Continuous B-Spline Kernels. In: \emph{Computer Vision and Pattern Recognition (CVPR)}.}{\faCalendar~\emph{2018}}

\ressubheading{Christian Eichhorn, \textbf{Matthias Fey}, Gabriele Kern-Isberner. CP- and OCF-networks – A Comparison. In \textit{Fuzzy Sets and Systems, Volume 298: Special Issue on Graded Logical Approaches and Their Applications.}}{\faCalendar~\emph{2016}}

\end{document}
